%!TEX program = xelatex
\documentclass[margin,line]{res}

%beginfont

% \usepackage[sfdefault]{roboto}
% \usepackage[T1]{fontenc}
%

% \usepackage{fontspec}

% \setmainfont{Barlow-Regular}[
%   Extension=.otf,
%   % other options
% ]

%endfont

\usepackage{hyperref}
\usepackage{xurl}

\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in
% if using pdflatex:
\setlength{\pdfpagewidth}{\paperwidth}
\setlength{\pdfpageheight}{\paperheight}

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.2in}} \raggedright}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.2in}} \raggedright}{\end{list}}


\begin{document}

% suppresses page numbers
\thispagestyle{empty}

\name{Maxime Alexander Sutters} % \vspace*{.1in}} 

\begin{resume}
\section{\sc Contact} % Information}
% \vspace{.05in}
% \begin{tabular}{@{}p{0.5in}p{2.78in}}
{\bf LinkedIn:} \url{https://www.linkedin.com/in/maxsutters}
{\bf Email:}  msutters@cs.washington.edu 
% {\it GitHub:} & https://github.com/maximelearning & {\it Phone:} (206) 321-0208 \\
% & speak{\textunderscore} candidate
% \end{tabular}

\section{\sc Experience}

{\bf Amazon}, Seattle/Bellevue, Washington USA \newline
{\em Software Development Engineer} \hfill {\bf January 2025 - December 2025} \newline
% roughly 01/13/2025 to 12/01/2025

\begin{list2}
\item Financial compliance driver and feature lead on a cross-team fullstack Java project using Amazon Lambda, SQS, SNS, and GraphQL backend APIs over AppSync served to a JavaScript/HTML front end. Made Amazon's global promotion management and accounting platform SOX-compliant by designing and implementing mandatory finance and accounting approvals.
\item Continued backend Java development work on data flows between customer shipping promotions management and accounting systems at Amazon.
\end{list2}

{\bf Amazon Web Services (AWS)}, Seattle/Bellevue, Washington USA \\
{\em Software Development Engineer Apprentice} \hfill {\bf June 2022 - April 2024} \\
% 06/27/2022 to 04/18/2024
\begin{list2}
%1
\item Developed feature to automate key security tasks within AWS datacenters worldwide. Key performance indicators included efficiency of contract guard force and site security management in protecting server hosts and locating events potentially exposing customer data. Designed and implemented project using Python, GraphQL, and Java and considered localization requirements and governmental edge cases. Drove work across two teams and designed tests and proofs of concept to ensure compliance and efficacy ahead of release.
%2
\item Maintained computer vision and machine learning systems processing petabytes of HTTP Live Streaming (HLS) video frames in real time and training and evaluating model performance against ground truth data. Automated jobs to locate cameras and sites for specific regions.
%3
\item Identified and resolved database query issues in legacy code with new SQL queries to Amazon Redshift databases.
%4
\item Built CloudWatch metrics, dashboards, and alarms to parse logs and monitor automated \\ Distributed Job Scheduler (DJS) jobs and AWS Lambda health and performance.
%5
\item Created and monitored CI/CD pipelines, AWS accounts, and Apollo environments for my team's daily code deployments. Facilitated host patching, permissions management, and code reusability.
\end{list2}
% Spinning up hosts to execute code, creating accounts 

% highlight core competencies of a software engineer - this should be about 30% of the whole resume

%
%\section{\sc Interests}
% Computer science education, inclusive hardware and software design, game development
% \vspace{-.3cm}
%
\section{\sc Education}

% GPA: {\bf 3.3}
{\bf University of Washington}, Seattle, Washington USA \hfill B.S. in Computer Engineering \\
% GPA: {\bf 3.93}
{\em Paul G. Allen School of Computer Science \& Engineering} \hfill Graduated {\bf December 2021} 

%\vspace*{-.3cm}
% \vspace*{.1cm}
% \begin{list1}
% \item[] B.S., Computer Engineering, December 2021
% % \item[] Relevant Courses: Networks, Systems, Digital Design, Compilers, Data Structures and Parallelism
% % \item[] Selected Courses: Networking, Systems, Data Structures and Parallelism, Compilers
% \end{list1}

% {\bf Seattle Central College}, Seattle, Washington USA %\hfill GPA: {\bf 3.93}
% \\

% % \vspace*{-.3cm}
% \begin{list1}
% \item[] A.S., Computer Science \& Engineering, June 2019
% \item[] Selected Courses: Computer Programming, Engineering Physics I-III, Computers in Math
% \end{list1}

% \vspace{-.2cm}
\section{\sc Skills} % Technical?
  {\em Programming Languages \& Frameworks}:  
  Python, Java, JavaScript, C, Bash, SQL, Assembly, HDL (Verilog/SystemVerilog), JSON  
  \\
  {\em Developer Tools}:  
  Git/GitLab, Vim, IntelliJ IDEA, GDB, LATEX, Mathematica, KiCad  
  \\
  {\em Cloud \& DevOps (AWS)}:  
  Lambda, API Gateway, DynamoDB, S3, Athena, Secrets Manager, Code Pipelines, GraphQL  
  \\
  {\em Operating Systems}:  
  Unix/Linux (Amazon Linux 2, Windows Subsystem for Linux), Windows  
  \\
  {\em Hardware \& Electronics}:  
  PCB design, 3D printing, Arduino/STM32 flashing, soldering/reflow

\section{\sc Projects }

{\bf GuitXR: \url{https://uwrealitylab.github.io/xrcapstone21sp-team4/}} %, CSE 481 V
\begin{list2}
\item AR guitar learning application for the Magic Leap headset with floating chords and tabs, instrument-mounted controls, and real-time pitch detection
\item Built in Javascript and HTML via the WebXR API and A-Frame web framework
\item Refactored ML5.js-based pitch recognition library for guitar
% to enable real-time feedback on played notes
\item Presented completed VR capstone demo at the University of Washington Reality Lab
\end{list2}

% {\bf N-Car Parking Garage Simulator (FPGA Test Design Verification)}
% \begin{list2}
% \item Designed and programmed finite state machine (FSM) logic in SystemVerilog for two presence sensors at the gate of a simulated parking garage and an n-bit counter to track available spots
% \item Simulated functionality of hardware devices (LEDs, seven-segment displays, buttons, and switches) in ModelSim before flashing to the Altera DE1{\textunderscore}SoC FPGA board using Quartus
% \end{list2}

% {\bf Tetris} %, CSC 143 (arcade game remake?)
% \begin{list2}
% \item Developed Tetris clone with advanced object-oriented programming (OOP) in Java
% \item Reinforced understanding of composition, inheritance, and model-view-controller (MVC)
% \item Applied skills in unit testing, version control through Git, and pair programming
% \end{list2}

% \section{\sc Algorithms \& ML Projects}
% 		\begin{list2}
%     \item Spam filter using Naive Bayes
%     \item KD-tree nearest neighbor finder
%     \item Content-aware image resizing using A* graph search
%     \end{list2}

\end{resume}
\end{document}




